Data Archiving Attitudes

### 2015-05-24 analysis.Rmd
Added more exploratory plots, and fixed a few quirks in data pre-processing.

@@

@@

<!-- Field: Q9 -->
4. To your knowledge, how often have you experienced the following situations as a result of sharing the datasets behind your published research with investigators outside your research groups? Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
  a.  I formed new collaborations <!-- Field: Q9_1 -->
	b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 -->
	c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 -->
	d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 -->
	e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 -->
	f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 -->
	g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 -->
	h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 -->
	i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 -->
	j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 -->
	k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 -->
	l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 -->
	m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 -->
	n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 -->
	o.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 -->
	p.  Other (please specify) <!-- Field: Q9_16 / Q9_16_TEXT -->

@@

<!-- Field: Q12 -->
6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
	a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
	b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
	c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
	d.  I don't know   <!-- Field: Q12_4 -->
	e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
	f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->

@@

@@

<!-- Field: Q18 -->
10. Imagine you just found a great journal to target when submitting your next manuscript. You read the Instruction to Authors and discover the journal adheres to the Joint Data Archiving Policy (above). How strongly do you disagree/agree with the following statements? I am worried that ...
	a.  others might do research I am currently working on  <!-- Field: Q18_1 -->
	b.  others might do research I am planning to do  <!-- Field: Q18_2 -->
	c.  others might find errors in my research  <!-- Field: Q18_3  -->
	d.  others might misinterpret my dataset or use it inappropriately  <!-- Field: Q18_4 -->
	e.  I/we might be bothered with a lot of questions by qualified people  <!-- Field: Q18_5 -->
	f.  I/we might be bothered with a lot of questions by unqualified people  <!-- Field: Q18_6 -->
	g.  I/we might not be able to find the data  <!-- Field: Q18_7 -->
	h.  it might take me/us a lot of time to find the data  <!-- Field: Q18_8 -->
	i.  it might take me/us a lot of time to format or document the data  <!-- Field: Q18_9 -->
	j.  it might take me/us a lot of time to submit the data  <!-- Field:  Q18_10-->
	k.  I might lose intellectual property or commercial opportunities  <!-- Field: Q18_11 -->
	l.  Other worries (please specify)  <!-- Field: Q18_12/Q18_12_TEXT -->

@@

## Questions 1, 2, 9
1. It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles. Include data sharing that occurs by any mechanism (e.g. emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
2. It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.

tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

## Questions 3
3. Do any of your published research papers have publicly archived datasets?

responses <- c("5+ papers","2-4 papers","1 paper","None") # response categories from top to bottom
tmp <- melt(d, measure.vars=c('Q_3'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="None", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

## Questions 4
4. To your knowledge, how often have you experienced the following situations as a result of sharing the datasets behind your published research with investigators outside your research groups? Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
  a.  I formed new collaborations <!-- Field: Q9_1 -->
        b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 -->
        c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 -->
        d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 -->
        e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 -->
        f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 -->
        g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 -->
        h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 -->
        i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 -->
        j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 -->
        k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 -->
        l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 -->
        m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 -->
        n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 -->
        o.  Other (please specify) <!-- Field: Q9_16 / Q9_16_TEXT -->
        p.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 -->

unique( d$Q_4_17 )
unique(as.character(d$Q_4_3))
1:15
responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom

tmp <- melt(d, measure.vars=paste0('Q_4_',c(1:15,17) ))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Never", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)

@@

<!-- TODO: Need to reformat data to analyze questions 6 (->Q12), 7 (->Q13),  -->

## Questions 6
6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
  a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
  b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
  c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
	d.  I don't know   <!-- Field: Q12_4 -->
	e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
	f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->

library(ggplot2)
library(reshape2)

d$Q_6_

with(d, xtabs(~I(Q_6_1!="")+I(Q_6_2!="")+I(Q_6_3!="") ))

unique( d$Q_8_2 )

@@

>>>>

_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_

@@

_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_

tmp <- melt(d, measure.vars=c('Q_1','Q_2'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

@@

  Response Options:
  1. Yes, datasets from <b>5 or more papers</b> are publicly available on the internet
  2. Yes, datasets from <b>2-4 papers</b> are publicly available on the internet
  3. Yes, a dataset from <b>one paper</b> is publicly available on the internet  
  4. No, none of my paper-related datasets are publicly available on the internet
  5. I've never published a paper based on a dataset collected by me or my co-authors
  6. I'm not sure if any of my papers have publicly available datasets

responses <- c("5+ papers with archived data","2-4 papers with archived data","1 paper with archived data","No papers with archived data") # response categories from top to bottom
tmp <- melt(d, measure.vars=c('Q_3'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="1 paper with archived data", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

<!-- Field: Q9 -->
4. To your knowledge, how often have you experienced the following situations as a result of sharing the datasets behind your published research with investigators outside your research groups? Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
  a.  I formed new collaborations <!-- Field: Q9_1 / Q_4_1 -->
	b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 / Q_4_2 -->
	c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 / Q_4_3 -->
	d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 / Q_4_4 -->
	e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 / Q_4_5 -->
	f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 / Q_4_6 -->
	g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 / Q_4_7 -->
	h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 / Q_4_8 -->
	i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 / Q_4_9 -->
	j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 / Q_4_10 -->
	k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 / Q_4_11 -->
	l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 / Q_4_12 -->
	m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 / Q_4_13 -->
	n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 / Q_4_14 -->
	o.  Other (please specify) <!-- Field: Q9_16 - Q9_16_TEXT / Q_4_15 - Q_4_15_TEXT -->
  p.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 / Q_4_16 -->

  Response Options:
  1. Many times
  2. A few times
  3. Once
  4. Never

responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
tmp <- melt(d, measure.vars=paste0('Q_4_',1:16 ))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
tmp <- melt(d, measure.vars=paste0('Q_5_', 1:3))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
#p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

<!-- Field: Q12 -->
6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?

Response options:
	a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
	b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
	c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
	d.  I don't know   <!-- Field: Q12_4 -->
	e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
	f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->

id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
cur_d$variable <- NULL

d$Q_6

levels <- c("ALL datasets are publicly available online","SOME but not all of the datasets are publicly available online",
            "NONE of the datasets are publicly available online","We did not collect any data for that publication",
            "I don't know", "Other (please specify)")
cur_d$value <- ordered(cur_d$value, levels=levels)

x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")

p + theme_bw()

@@

id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
cur_d <- d[,c(id_vars,paste0('Q_7_', 1:6))]
cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
cur_d$variable <- NULL

levels <- c("Journal supplementary information", "A repository for data or research output", "A personal or lab website",
            "The entire dataset is in the body of the paper", "Not applicable", "Other (please specify)")
cur_d$value <- ordered(cur_d$value, levels=levels)

x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")

p + theme_bw()

@@

Response options:
  i. Strongly Agree
  ii. Agree
  iii. Somewhat Agree
  iv. Neutral
  v. Somewhat Disagree
  vi. Disagree
  vii. Strongly Disagree

```{r, fig.width=5, fig.height=5, echo=FALSE}

tmp <- melt(d, measure.vars=c('Q_9'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

```
<!-- Field: Q18 -->
10. Imagine you just found a great journal to target when submitting your next manuscript. You read the Instruction to Authors and discover the journal adheres to the Joint Data Archiving Policy (above). How strongly do you disagree/agree with the following statements? I am worried that ...
	a.  others might do research I am currently working on  <!-- Field: Q18_1 -->
	b.  others might do research I am planning to do  <!-- Field: Q18_2 -->
	c.  others might find errors in my research  <!-- Field: Q18_3  -->
	d.  others might misinterpret my dataset or use it inappropriately  <!-- Field: Q18_4 -->
	e.  I/we might be bothered with a lot of questions by qualified people  <!-- Field: Q18_5 -->
	f.  I/we might be bothered with a lot of questions by unqualified people  <!-- Field: Q18_6 -->
	g.  I/we might not be able to find the data  <!-- Field: Q18_7 -->
	h.  it might take me/us a lot of time to find the data  <!-- Field: Q18_8 -->
	i.  it might take me/us a lot of time to format or document the data  <!-- Field: Q18_9 -->
	j.  it might take me/us a lot of time to submit the data  <!-- Field:  Q18_10-->
	k.  I might lose intellectual property or commercial opportunities  <!-- Field: Q18_11 -->
	l.  Other worries (please specify)  <!-- Field: Q18_12/Q18_12_TEXT -->

@@

@@

## Questions 6
6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
  b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
  c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
  d.  I don't know   <!-- Field: Q12_4 -->
e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
<!-- TODO: What is d$Q_6_7 ??? -->

```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}

library(ggplot2)
library(reshape2)
library(plyr)
library(dplyr)
library(vcd)

cnames <- paste0('Q_6_',1:6)
x <- d[,cnames]
new_cnames <- apply(x, 2, function(x) unique(x[x!=""])) 
colnames(x) <- new_cnames
x <- x!=""
x

res <- apply(x, 2, function(c1) apply(x, 2, function(c2) sum(c1&c2) ))
res[lower.tri(res)] <- NA
diag(res) <- NA
res

@@

```{r, eval=FALSE, fig.width=7, fig.height=5, echo=FALSE}
